comgen-outline

### 2017-08-10 paper/comgen-paper.Rmd
minor changes

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.

>>>>

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial to trhiving in an open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just rare (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
By sharing painfully-won generalizations we thrive collectively without individually needing to taste each potentialy-poisonous plant or witness enough lightning strikes.
